\documentclass[letterpaper,12pt]{article}

\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{a4wide}
\usepackage{graphicx}
\usepackage{epsfig}

\begin{document}

\title{Skills And Attributes File Description}

\author{
DNTeam
}

\maketitle

\abstract{\begin{center}This document describes the Skills and Attributes files Struct
          \end{center}}

\newpage

\tableofcontents

\newpage


\section{Introduction}

The skills on DccNiTghtmare have a lot of uses and are, with the attributes,
the real base of the {\it DNT20+1 System}. This is the reason to put the two at
the same struct: they have the same way to look at and somewhat the same
usuability.

\section{Skills/Attributes File}

All skills and attributes on DNT have the same file struct, as described bellow:

\begin{verbatim}
Name
Description
Base Attribute
\end{verbatim}

\subsection{Name}
{\bf Type:} String;\\
It's the name of the skill or attribute.

\subsection{Description}
{\bf Type:} String;\\
It's the description of the skill or attribute, in only one line, divided by '|' to change lines on the game (usually at each 39 characters).

\subsection{Base Attribute}
{\bf Type:} String (without spaces);\\
It's the base attribute of the skill (or the attribute of the attribute itself). For example:

\begin{verbatim}
INTELLIGENCE
\end{verbatim}

\section{Skills/Attributes List}

The list of skills is like any other DNT descriptions list, as bellow:

\begin{verbatim}
Number_of_Skills
skill_index skill_file skill_image skill_internal_name
\end{verbatim}

\subsection{Number of Skills}
{\bf Type:} Integer;\\
The total number of skills avaible on the game.

\subsection{Skill Index}
{\bf Type:} Integer;\\
The vector Index of the skill.

\subsection{Skill File}
{\bf Type:} String (without spaces);\\
The filename of the skill, relative to the ./bin folder.

\subsection{Skill Image}
{\bf Type:} String (without spaces);\\
The skill image filename of the skill, relative to the ./bin folder.

\subsection{Skill Internal Name}
{\bf Type:} String (without spaces);\\
The Skill internal name. It's the Skill ID that will be used any time requerided
by the definitions files.

\end{document}

